Local Search, Brute-Force and Recursion for Selection Operator\thanks{This work was not supported by Velbazhd Software LLC and Bulgarian Ministry of Education and Science.}

### 2020-04-10 Local-Search-Brute-Force-and-Recursion-for-Selection-Operator/paper.tex
Part of the introduction was written.

>>>>

In the field of meta-heuristic global optimization, genetic algorithms are well known and widely applied. Genetic algorithms have stochastic nature because random or pseudo-random numbers are extensively used in common operators like crossover, mutation, and selection. Finding global optimum is rarely possible and in most cases, genetic algorithms give sub-optimal solutions. Because of the stochastic nature found solutions can differ between different runs of the optimization process. At the same time, the possibilities for different runs are great option for parallel or distributed computing. Mechanisms in natural evolution have inspired the ideas involved in genetic algorithms. Meta-heuristics are most useful for optimization problems in multidimensional spaces with a high degree of non-linearity. A point in multidimensional space (for genetic algorithms it is the solutions space) is presented as vector of values. The set of vectors in the solutions space forms a population of individuals in terms of genetic algorithms. The size of the population is very problem dependent and it is estimated empirically by trial and error approach. The target function is applied to each individual of the population. The result of this calculation gives the individual's fitness value. The fitness value gets better with approaching the optimum. Individuals with better fitness have better chances to mate and to form a new generation. The mating process consists of two common operators - crossover and mutation. Crossover contributes to the exploration of the solutions space when mutation contributes to the exploitation of the solutions space. Genetic algorithms are heavily researched in the last few decades, but there are still directions for improvements. Such direction is the selection operator. This research focuses on searching for optimum to set of benchmark functions by the addition of local search in brute-force procedure when it is applied in recursive descent.
